Integrated farming and global warming mitigation in Brazil

### 2022-07-29 manuscript/manuscript.qmd
Change methods diagram.

```{r}
#| include: false
  library(nomnoml)
```

---

@@

---

@@

4. Can further expansion of ICLFS, beyond Brazil’s NDC target, replace the afforestation targets pledged in the scientific literature for the tropics in terms of carbon storage, provision of ecosystem services and economic revenue?

---

@@

```{nomnoml}
#| echo: false

# direction: down
# .box: dashed
[Start]-[Finish!]
[Finish!]-[<box>blablablablabla
           lablablablablablabla]

@@

### Model projections

---

>>>>

```{r}
#| include: false

library(DiagrammeR)
```

------------------------------------------------------------------------

@@

------------------------------------------------------------------------

@@

4.  Can further expansion of ICLFS, beyond Brazil's NDC target, replace the afforestation targets pledged in the scientific literature for the tropics in terms of carbon storage, provision of ecosystem services and economic revenue?

------------------------------------------------------------------------

@@

```{r}
#| echo: false

grViz(
  "digraph {

  graph [layout = dot, rankdir = TD, nodesep = 1.2, ranksep = 0.12]

  node [shape = box,
        fontname = Helvetica,
        style = filled,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 1.2,
        fontsize = 11]

  a [label = 'Literature \n Review']
  b [label = 'Experts \n Survey']
  c [label = 'ICLF \n Database']
  d [label = 'Modelling \n Scenarios']
  e [label = 'ICLF \n Expantion \n Projections']
  f [label = 'Services \n Estimations']

  a -> {b c} b -> c
  c -> {d e f} d -> e 
  e -> f

  }"
)

@@

#### Integrated crop-livestock-forest database

### Model framework

#### Modelling scenarios

#### Integrated crop-livestock-forest expansion projections

#### Services estimations

------------------------------------------------------------------------
